SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-13 paper/pm-1-matrix.tex
more stuff
fixed-dia
my changes
more new

\begin{figure}
\centering
\begin{minipage}{0.45\linewidth}
  \hspace{-4ex}
\begin{tikzpicture}
\matrix [matrix of math nodes,left delimiter=(,right delimiter=),row sep=0.16cm,column sep=0.1cm] (m) {
\times & \times & \times &\times&\times&\times & \times & \times\\
\times & \times & \times&\times&\times&\times& 1 &\times \\
\times & \times & \times&\times&\times&1&\times &\times\\
\times & \times & \times&\times & 1 & \times &\times & \times\\
 \times & \times & \times & \times & \times & \times & \times & \times\\
 \times & \times & \times &\times & \times & \times & \times & \times\\
 \times & \times & \times & \times & \times & \times & \times & \times\\
 \times & \times & \times & \times & \times & \times&\times & \times\\};

@@

\end{tikzpicture}  
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \tikzset{
    ln/.style  = { draw, thick, fill=black, circle, inner sep=0.3mm},
    sqloc/.style  = { draw, thick, inner sep=1.0mm },
    loc/.style    = { draw, circle, thick, inner sep=1.0mm },
  }
\begin{tikzpicture}[node distance = 30mm]
  \node[draw] (n0) {$n_1:\{01234\}$};
  \node[draw,below left of=n0] (n1) {$n_0:\{01236\}$};
  \node[draw,below right of=n0] (n2) {$n_2:\{012368\}$};

  \draw[->,thick] (n1) -- node[left=1mm]  {$01$} (n0);
  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$013$} (n0);
  \draw [->,thick] (n0) to [bend right=-30] node[below=2pt,xshift=3pt]  {$013$} (n1);

>>>>

\begin{figure}
\centering
\begin{minipage}{0.50\linewidth}
  \hspace{-4ex}
\begin{tikzpicture}
\matrix [matrix of math nodes,left delimiter=(,right delimiter=),row sep=0.16cm,column sep=0.1cm] (m) {
\times & \times & \times &\times&\times&\times & \times & \times\\
\times & \times & \times&\times&\times&\times& 1 &\times \\
\times & \times & \times&\times&\times&1&\times &\times\\
\times & \times & \times&\times & 1 & \times &\times & \times\\
 \times & \times & \times & \times & \times & \times & \times & \times\\
 \times & \times & \times &\times & \times & \times & \times & \times\\
 \times & \times & \times & \times & \times & \times & \times & \times\\
 \times & \times & \times & \times & \times & \times&\times & \times\\};

@@

\end{tikzpicture}  
\end{minipage}
\begin{minipage}{0.45\linewidth}

\begin{tikzpicture}[node distance = 30mm]
  \node[draw] (n0) {$n_1:\overline{01234}$};
  \node[draw,below left of=n0] (n1) {$n_0:\overline{01236}$};
  \node[draw,below right of=n0] (n2) {$n_2:\overline{012368}$};

  \draw[->,thick] (n1) -- node[left=1mm]  {$0\overline{1}$} (n0);
  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$\overline{01}23$} (n0);
  \draw [->,thick] (n0) to [bend right=-30] node[below=2pt,xshift=3pt]  {$013$} (n1);
